### 2018-12-09 reports/thesis/chapters/5_inference.tex
Started writing on noContamination experiment
tex: made command /addNumber which inputs a text file protected and without space at the end
.eps figures are saved in allNullGaussian
.txt files are saved in allNullGaussian
new figures in allNullGaussian

>>>>

\subsection{Uncontaminated Experiment}
The empirical null filter was demonstrated on a $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ image where each pixel has $\normal(0,1)$ test statistics. The test statistics after filtering should preserve its original distribution, or at least close to it. An experiment was conducted to investigate the empirical properties when filtering such as an image.

An example of the Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt} is shown in Figure \ref{fig:inference_noContamination_images}. A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal. Because the empirical null mean and empirical null standard deviation are non-Normal random variables, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.

In this experiment, the sample mean and sample variance of the pre/post filtered test statistics were investigated.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/inference/noContamination/qq.eps}
	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
	\label{fig:inference_noContamination_qq}
\end{figure}

\begin{figure}[p]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/unfiltered.eps}
		\caption{Unfiltered}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/filtered.eps}
		\caption{Filtered}
	\end{subfigure}
	\caption{A $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
	\label{fig:inference_noContamination_images}
\end{figure}

\begin{figure}[p]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/nullmean.eps}
		\caption{Empirical null mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/noContamination/nullstd.eps}
		\caption{Empirical null std}
	\end{subfigure}
	\caption{The empirical null parameters when filtering a $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt}.}
	\label{fig:inference_noContamination_nullimages}
\end{figure}

\subsection{Contaminated Experiment}

\subsection{Contaminated Defect Experiment}
